Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-26 ms.tex
another dramatic display of what happens if a horizontally-displayed aperture is used.

>>>>

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_side_backsub_removelinear_True_3.pdf}{0.48\textwidth}{Allan Variance}}
\caption{The same test as Figure \ref{fig:GLtSeriesAcrossDetectors} shows {\bf dramatically} smaller noise if (1) the aperture size is increased and (2) a horizontally displaced aperture is used to reduce 1/f noise.}\label{fig:GLtSeriesRun112}
\end{figure*}
